---
title: "Discussion About Shiny Application"
author: "Yunshu Zhang"
format: pdf
thanks: "Code and data are available at: https://github.com/Yunshu921/shiny.git. The app is available at: https://posit.cloud/content/7924192."
date: today
date-format: long
editor: visual
toc: TRUE
number-sections: true
bibliography: references.bib
---
# Background

The ideas discussed in Bouie [@2022] state that we should identify ethical issues while dealing with the quantitative analysis of human atrocity. Something has to be present during the quantification process that we disregard. Put another way, there is never a flawless data set that is complete, regardless of how precise and comprehensive the set is. As a result, we aim to achieve the stated objective: resolve some moral issues.

During World War II and the Holocaust, Auschwitz concentration camp was a major place of the Nazis' Final Solution to the Jewish problem [@Wiki].

# Application Findings

I use `shiny` [@citeshiny] to make a interactive graph and table. See details of my app at: https://posit.cloud/content/7924192. These show the number of victims murdered by religion and  the user is allowed to specify the religions they are interested in seeing data for.

What's more, I use `ggplot2` function to make @fig-1 to show the number of victims for each religion. 







```{r setup, include=FALSE}
# Load libraries
library(shiny)
library(dplyr)
library(ggplot2)

setwd("/cloud/project")


# Read data
data <- read.csv("originaldata.csv")
```
In the @fig-1, we can found that the number of victims who has religion Catholic is larger than that of religion Jewish. Usually we think the Holocaust killed Jewish most, but this graph shows a different thing. Thus we can infer some reasons behind this fact.
And this finding shows the crudity of the Holocaust indirectly.

Firstly, one of reasons is a lack of empathy and awareness of human connection. Secondly, persecution may begin with small-scale, targeted crimes, but if harassment is allowed to continue, it can intensify until it becomes uncontrollable. The morals and sympathy of those executing the atrocities gradually diminish throughout this process. The effect that follows is disastrous.

Lastly, just like as Bouie said [@2022], Even though there are not many monuments honoring the victims of Auschwitz and there is not enough information available about their experiences, every single one of them was a live, breathing person, just like the people we honor with statues.

It is imperative that we keep the truth of their innate humanity at the center of what we do, even as we learn new facts and apply innovative techniques. To avoid repeating the dehumanization that took place inside the walls of the concentration camp, we must approach their history with consciousness, empathy, and reverence.


```{r}
#| label: fig-1
#| fig-cap: The number of victims for each religion
#| echo: false
#| warning: false

#Count number of victims by religion
victim_counts <- table(data$Religion)
#Convert the counts to a data frame
victim_counts_df <- data.frame(Religion = names(victim_counts), Count = as.numeric(victim_counts))
#Create a grap using ggplot2

ggplot(victim_counts_df, aes(x = Religion, y = Count)) +
  geom_col(fill = "skyblue", color = "black") +
  labs(title = "Holocaust Victims by Religion",
       x = "Religion",
       y = "Number of Victims") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  coord_flip()



```


