---
title: "Discussion About Shiny Application"
author: "Yunshu Zhang"
format: pdf
thanks: "Code and data are available at: https://github.com/Yunshu921/shiny.git. The app is available at: https://posit.cloud/content/7924192."
date: today
date-format: long
editor: visual
toc: TRUE
number-sections: true
bibliography: references.bib
---
# Background

The ideas discussed in Bouie [@2022] state that we should identify ethical issues while dealing with the quantitative analysis of human atrocity. Something has to be present during the quantification process that we disregard. Put another way, there is never a flawless data set that is complete, regardless of how precise and comprehensive the set is. As a result, we aim to achieve the stated objective: resolve some moral issues.

During World War II and the Holocaust, Auschwitz concentration camp was a major place of the Nazis' Final Solution to the Jewish problem [@Wiki].

# Application Findings

I use `shiny` [@citeshiny] to make a interactive graph and table. See details of my app at: https://posit.cloud/content/7924192. These show the number of victims murdered by religion and  the user is allowed to specify the religions they are interested in seeing data for.

What's more, I use `ggplot2` function to make @fig-1 to show the number of victims for each religion. 







```{r setup, include=FALSE}
# Load libraries
library(shiny)
library(dplyr)
library(ggplot2)

setwd("/cloud/project")


# Read data
data <- read.csv("originaldata.csv")
```
In the @fig-1, we can found that the number of victims who has religion Catholic is larger than that of religion Jewish. Usually we think the Holocaust killed Jewish most, but this graph shows a different thing. Thus we can infer some reasons behind this fact.
And this finding shows the crudity of the Holocaust indirectly.

```{r}
#| label: fig-1
#| fig-cap: The number of victims for each religion
#| echo: false
#| warning: false

#Count number of victims by religion
victim_counts <- table(data$Religion)
#Convert the counts to a data frame
victim_counts_df <- data.frame(Religion = names(victim_counts), Count = as.numeric(victim_counts))
#Create a grap using ggplot2

ggplot(victim_counts_df, aes(x = Religion, y = Count)) +
  geom_col(fill = "skyblue", color = "black") +
  labs(title = "Holocaust Victims by Religion",
       x = "Religion",
       y = "Number of Victims") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  coord_flip()



```


